Adolescent well-being in the digital age

### 2022-01-31 associations.Rmd
Use .Rmd

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  mutate(
    fit1 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
    ),
    fit2 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
    )
  )
```

@@

```{r model21-compare}
#| results: hold
#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
#| label: tbl-m12-r2

fits %>%
  select(outcome, fit1, fit2) %>% 
  pivot_longer(c(fit1, fit2)) %>% 
  mutate(
    r2 = map(
      value,
      ~ bayes_R2(., resp = "val") %>%
        as.data.frame() %>%
        mutate(across(everything(), ~ percent(., .1))) %>%
        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
    )
  ) %>%
  select(-value) %>%
  unnest(r2) %>% 
  pivot_wider(
    names_from = name,
    values_from = result,
    names_prefix = "Model "
  ) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  kbl(caption = "Model 1 and 2 R-squared values") %>%
  kable_custom()
fits <- select(fits, -fit1)
```

@@

p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x"
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
```

This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small. First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`. However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%. Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region. However, none of the average associations were credibly different from zero. The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.

@@

fitted_country <- function(x) {
  newx <- x$data %>%
    group_by(country) %>%
    mutate(
      xmin = min(i1_cw, na.rm = TRUE),
      xmax = max(i1_cw, na.rm = TRUE)
    ) %>%
    filter(i1_cw %in% c(xmin, xmax)) %>%
    ungroup() %>%
    distinct(country, region, outcome, i1_cw, i1_cb) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)
  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
    select(-outcome)
  newy
}

fitted_region <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region) %>%
    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = ~ 
          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
        )
    )
  ) %>%
    select(-outcome)
  newy
}

@@

f_country %>%
  ggplot(aes(i1_cw, Estimate)) +
  scale_x_continuous(
    "Previous year's internet adoption relative to country average in 2000-2020",
    breaks = c(-.35, 0, .35),
    labels = function(x) percent(x, 1)
  ) +
  scale_y_continuous(
    "Estimate",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
  ) +
  geom_blank() +
  geom_ribbon(
    data = f_region,
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .15, fill = "dodgerblue4"
  ) +
  geom_line(
    data = f_region,
    col = "dodgerblue4", size = .6
  ) +
  geom_line(
    aes(group = country),
    size = .4, alpha = .35, col = "dodgerblue1"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    panel.spacing = unit(2, "pt"),
    axis.title.y = element_blank()
  )
```

@@

fitted_cb1 <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region, country) %>%
    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = NA
        )
    )
  ) %>%
    select(-outcome)
  newy
}
tmp <- fits %>% 
  mutate(out = map(fit2, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)

>>>>

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  mutate(
    fit2 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
    )
  )
```

@@

```{r model21-compare}
#| results: hold
#| tbl-cap: "Model 1 and 2 proportions variance explained"
#| label: tbl-m12-r2

# Takes a while so save to file
r2_file_path <- "models/m12r2.rds"
if (!file.exists(r2_file_path)) {
  fits <- fits %>% 
    mutate(
      fit1 = map(
        outcome, 
        ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
      )
    )

  r2_tab <- fits %>%
    select(outcome, fit1, fit2) %>% 
    pivot_longer(c(fit1, fit2)) %>% 
    mutate(
      r2 = map(
        value,
        ~ bayes_R2(., resp = "val") %>%
          as.data.frame() %>%
          mutate(across(everything(), ~ percent(., .1))) %>%
          transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
      )
    ) %>%
    select(-value) %>%
    unnest(r2) %>% 
    pivot_wider(
      names_from = name,
      values_from = result,
      names_prefix = "Model "
    ) %>%
    mutate(outcome = str_replace(outcome, "_", " "))
  write_rds(r2_tab, r2_file_path)
  fits <- select(fits, -fit1)
} else {r2_tab <- read_rds(r2_file_path)}

r2_tab %>% 
  kbl(caption = "Model 1 and 2 R-squared values") %>%
  kable_custom()

read_docx() %>% 
  body_add_table(
    r2_tab,
    first_column = TRUE
  ) %>% 
  print("Table-R2.docx")
```

@@

p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional lagged effect of 10% increase in internet adoption",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 1000, .001) %>% 
      str_remove("\\.000") %>% 
      # Remove trailing zero (twice)
      str_remove("(?<=[:digit:])0(?=%)") %>% 
      str_remove("(?<=[:digit:])0(?=%)"),
    expand = expansion(c(.15, .15))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      filter(!(outcome=="Selfharm" & abs(Estimate) > .05)) %>% 
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 1000, .0001),
            percent(. / 1000, .01)
          )
        )
      ),
    family = Font, lineheight = 1,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x"
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    panel.spacing.x = unit(10, "pt"), 
    plot.margin = unit(rep(10, 4), "pt"),
    legend.position = "none"
  )
x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/1000)
x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)

# How many selfharm countries not shown on plot for clarity?
p_sums %>%
  filter(outcome=="Selfharm") %>% 
  drop_na(country) %>% 
  mutate(extreme = abs(Estimate) > .05) %>% 
  janitor::tabyl(extreme)

# Numbers
p_sums %>% 
  filter(region=="Average") %>% 
  mutate(across(where(is.numeric), ~percent(./1000, .0001))) %>% 
  transmute(
    outcome,
    result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]")
  )
```

This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small. First, on average across regions and countries, a 10% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`. However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%. Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region. However, none of the average associations were credibly different from zero. The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.

@@

fitted_country <- function(x) {
  newx <- x$data %>%
    group_by(country) %>%
    mutate(
      xmin = min(i1_cw, na.rm = TRUE),
      xmax = max(i1_cw, na.rm = TRUE)
    ) %>%
    filter(i1_cw %in% c(xmin, xmax)) %>%
    ungroup() %>%
    distinct(country, region, i1_cw, i1_cb) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)
  newy <- bind_cols(
    newx, 
    as.data.frame(fitted(x, newdata = newx))
  )
  newy
}

fitted_region <- function(x) {
  newx <- x$data %>%
    group_by(region) %>%
    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = ~ 
          (year * sex * age + i1_cw * sex * age | region)
        )
    )
  )
  newy
}

@@

f_country %>%
  ggplot(aes(i1_cw, Estimate)) +
  scale_x_continuous(
    "Previous year's internet adoption relative to country average in 2000-2020",
    breaks = c(-.35, 0, .35),
    labels = function(x) percent(x, 1)
  ) +
  scale_y_continuous(
    "Estimate",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
  ) +
  geom_blank() +
  geom_ribbon(
    data = f_region,
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .15, fill = "dodgerblue4"
  ) +
  geom_line(
    data = f_region,
    col = "dodgerblue4", size = .6
  ) +
  geom_line(
    aes(group = country),
    size = .4, alpha = .35, col = "dodgerblue1"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    panel.spacing = unit(2, "pt"),
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

@@

fitted_cb1 <- function(x) {
  newx <- x$data %>%
    group_by(region, country) %>%
    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = NA
        )
    )
  )
  newy
}
tmp <- fits %>% 
  mutate(out = map(fit2, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)
